---
title: "Introduction to ATC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_ATC}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
library("devtools")
library(repmis)
library(dplyr)
install_github('xiaozhouw/ATC')
```

The ATC package provides a function `findClass()` to help users find the corresponding ATC of one medication. Two lists will be returned. 
The first list contains a table that lists all the drugs that contained in the medication.
The second list contains one table for each drug and its corresponding classes under the selected tier.



*** 
### FUNCTION PROCEDURES
Based one the input medication string, output generating process varies. Three situations can be considered here. 

1. Medication exists in the record already.
    * Two tables can be generated only using the existed data, no need to use API.

2. Medication does not exist in the table, but its corresponding drugs do. For instance, different doses.
    * Two tables can also be generated only using the existed data since we only focus on the drug component.

3. Neither medication nor its corresponding drugs are in the tables. Regular expression is used to extract the drug component(s) in the medication, and the first table is being built accordingly.
    * If medication only contains one drug: the second list only contains one table that illustrates the classes of the drug.
    
    * If medication contains more than one (which is usually two) drugs: the second list will contain multiple tables.


***
### EXAMPLES
1. An already existed medication
```{r message=FALSE, warning=FALSE}
test_med = "fentanyl (pf) 50 mcg/ml injection solution"
test_tier = 4
findClass(test_med,test_tier)
```

2. A new medication but its drug is in the record
```{r message=FALSE, warning=FALSE}
test_med = "fentanyl (pf) 500 mcg/ml injection solution"
test_tier = 4
findClass(test_med,test_tier)
```

3. A new medication with 2 drugs (both drugs are in the record)
```{r message=FALSE, warning=FALSE}
test_med = "fentanyl-acetaminophen 50mg"
test_tier = 4
findClass(test_med,test_tier)
```
