---
title: "Introduction to ATC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_ATC}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
```{r}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
library("devtools")
install_github('xiaozhouw/ATC')
```

The ATC package provide a function `findClass()` to help users find the corresponding ATC of one medication.

*** 
### FUNCTION PROCEDURES
Based one the input medication string, output generating process varies. Three situations can be considered here. 

1. Medication exists in the table already.

2. Medication does not exist in the table but its corresponding drugs do.For instance, different doses.

3. Neither medication nor its corresponding drugs are in the tables
    * If medication only contains one drug.
    
    * If medication contains more than one (which is usually two) drugs.


***
## EXAMPLES
1. An already existed medication
```{r}
test_med = "fentanyl (pf) 50 mcg/ml injection solution"
test_tier = 4
findClass(test_med,test_tier)
```

2. A new medication but its drug is in the record
```{r}
test_med = "fentanyl (pf) 500 mcg/ml injection solution"
test_tier = 4
findClass(test_med,test_tier)
```

3. A new medication with 2 drugs (both drugs are in the record)
```{r}
test_med = "fentanyl-acetaminophen 50mg"
test_tier = 4
findClass(test_med,test_tier)
```
